\section{Introduction}
\label{ch:intro}
\noindent

\subsection{Background and problem motivation}
\label{ch:intro:problem-motivation}

IoT is a growing market in the world with MQTT and CoAP emerging as the dominant protocols for communication. Different IoT systems might need to communicate with one another event tho they might use different protocols. To do this a translator is needed to be able to translate CoAP to MQTT. 



\subsection{Overall aim}
\label{ch:intro:overall-aim}
The aim for this project is to implement a system that translates responses from a CoAP server to a MQTT client running on a mobile application. The scenario is to monitor the CoAP server system usage and prepare a system for future integration with temperature sensors. 


\subsection{Concrete and verifiable goals}
\label{ch:intro:verifiable-goals}
The goals for this project
\begin{itemize}
    \item Combine a MQTT-client with a CoAP-client for translation.
    \item Implement a CoAP-server capable of serving CPU, memory usage and mock temperature sensors.
    \item Create a user application capable of displaying the information.
    \item Perform measurements on the system for evaluation.
\end{itemize}

\subsection{Scope}
\label{ch:intro:scope}
This project will focus on implementing an end to end system from a CoAP-server to MQTT-client through a MQTT-broker. The only measurement that I will be conducting is the RTT from the client application to the CoAP-server from this the mean, min max and standard deviation will be calculated. From the total time for x amount of requests the request per second will be calculated.

\subsection{Outline}
\label{ch:intro:outline}
Chapter \ref{ch:theory} will go into theory about the technology used. Chapter \ref{ch:method} will motivate the technology choices as well as describe the system. Chapter \ref{ch:impl} will go through the construction process for the system. Chapter \ref{ch:results} will present the result from the measurements. Chapter \ref{ch:concl} will discuss the result as well as draw conclusion from this project.

\subsection{Contributions}
\label{ch:intro:contributions}
This project and report was done by me. External open-source packages was used to complete the project. All external packages are credited as citations.


